---
title: "*Deprivation per children* "
format: html
execute:
  echo: false
  warning: false
  message: false

output:
  html_document:
    css: styles.css
---

```{=html}
<style>
  body {
    background-color: lightpink;
    color: black;
  }
</style>
```
## Deprivation per Children:

For governments, international organizations, and politicians to effectively battle poverty, advance gender equality, and enhance the general well-being of children and populations globally, these indicators are essential. The intricate interaction of economic, social, and cultural elements that contributes to differences in access to opportunities and resources must be considered in any effort to combat poverty and inequality.

## DATA

```{r}
#| label: setup
#| include: false

#install.packages("tidyverse")
library(tidyverse)

#install.packages("ggplot2")
library(ggplot2)

#install.packages("maps")

library(ggplot2)

getwd()

unicef_indicator_1 <- read.csv("/cloud/project/Manisha/unicef_indicator_manisha.csv")
unicef_metadata <- read.csv("/cloud/project/Manisha/unicef_metadata.csv")

unicef_indicator_1 <- unicef_indicator_1 %>% 
  rename(year = time_period)

merged_data <- merge(unicef_indicator_1, unicef_metadata, by = c("country", "year"))
```

## Population Statistics

This statistic highlights the finding that there is a 0.39% disparity in the levels of deprivation experienced by children of each gender. This implies that disparate treatment or resource access based on gender may be caused by specific sociological or cultural variables. For children of all genders to have equal opportunities and rights, this gap must be closed.

```{r}
library(dplyr)
library(ggmap)

options(scipen = 999)

# Filter data for the year 2020
pop_2020 <- unicef_metadata %>% 
  filter(year == 2020)

# Load world map data
map_world <- map_data("world")

# Join population data with map data
map_pop_2020 <- full_join(map_world, pop_2020, by = c("region" = "country"))


# Define breaks and labels for the population scale
breaks <- c(0, 1e6, 2e6, 5e6, 1e7, 2e7, 5e7, 1e8)
labels <- scales::comma(breaks)
```

## World Map

```{r}
library(dplyr)
library(ggmap)

options(scipen = 999)

# Filter data for the year 2020
pop_2020 <- unicef_metadata %>% 
  filter(year == 2020)

# Load world map data
map_world <- map_data("world")

# Join population data with map data
map_pop_2020 <- full_join(map_world, pop_2020, by = c("region" = "country"))

# Define breaks and labels for the population scale
breaks <- seq(0, max(breaks), length.out = length(breaks))
labels <- scales::comma(breaks / 1e3)  # Display numbers in thousands (shorthand notation)
labels <- gsub(",", "", labels)  # Remove commas from labels
labels <- gsub("0(?=k$)", "", labels, perl = TRUE)  # Remove trailing zeroes before "k"

# Plot world population distribution
ggplot(data = map_pop_2020, aes(x = long, y = lat, group = group, fill = Population..total)) +
  geom_polygon(color = "black", size = 0.1) +  
  scale_fill_viridis_c(name = "Population (in 000s)", na.value = "grey90", 
                        breaks = breaks, labels = labels, limits = c(0, max(breaks))) +  
  labs(title = "World Population Distribution (2020)") +  
  theme_minimal() + 
  theme(plot.title = element_text(size = 16, hjust = 0.5),
        legend.position = "bottom",  # Position legend at the bottom
        legend.title = element_text(size = 12),  # Increase legend title size
        legend.text = element_text(size = 10),  # Increase legend text size
        legend.key.width = unit(2.5, "cm"),  # Increase legend key width for better display
        axis.text.x = element_blank(), axis.text.y = element_blank(),  
        axis.title.x = element_blank(), axis.title.y = element_blank())
```

## BAR CHART

```{r}



ggplot(unicef_indicator_1[unicef_indicator_1$sex != "Total", c("country", "obs_value", "sex")], aes(x = reorder(country, -obs_value), y = obs_value, fill = sex)) +
  geom_bar(stat = "identity") +
  labs(title = "Bar Chart", x = "Country", y = "sex") +
  theme(axis.text.x = element_text(angle =45, hjust = 1)) 


```

```{r}
library(ggplot2)

# Filter the dataframe to include only rows for Afghanistan
ireland_df <- unicef_metadata[unicef_metadata$country == "Ireland",]

# Create a time series chart
ggplot(ireland_df, aes(x = year, y = `Population..total`)) +
  geom_line() +
  labs(title = "Population of Ireland over time",
       x = "Year",
       y = "Population (total)") +
  theme_minimal()
```

```{r}

#new
ggplot(data = unicef_indicator_1, aes(x = year, y = obs_value)) +
  geom_point() +
  geom_smooth(method = "lm") +
 labs(title = "Scatter Plot", x = "Year", y = "GDP")
  
```

## Scatter Plot

A poorer economy is frequently indicated by a lower GDP per capita, and this can have a negative impact on many elements of life, including children's life expectancy. Children may be more vulnerable to malnutrition, receive less quality healthcare, and have less access to education in lower-income nations. These factors can have a detrimental effect on the health and wellbeing of children.
